Automated verification of electrical systems: literature review and case studies of stand-alone solar photovoltaics\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2019-01-21 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
fixed references
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\keywords{Automated verification  \and Model Checking \and Electrical systems \and Solar photovoltaic systems.}
\end{abstract}
%
%
%
\section{Introduction}
%%%%%In 2015, 193 Member States of the United Nations agreed as part of the Sustainable Development Goals (SDG) with a specific target to 'ensure access to affordable, reliable and modern energy for all by 2030' – universal access to electricity and clean cooking~\cite{IEAeao2017}. Therefore electricity has a important role, based on two main issues: %that are on the agenda of all current rulers and society in general, regardless of whether it is a developed, emerging or developing country: 
%%%%%the impact on the global climate change and poverty alleviation.
%
%%%%%Related to climate change, the 23rd session of the Conference of the Parties (COP23) to the United Nations Framework Convention on Climate Change (UNFCCC) in 2017 was the second session after the Paris Agreement, which aims to keep the maximum global average temperature rise as close as possible to 1.5 $^{o}$C. %During COP23, with respect to the future market development of renewable power and solar PV (photovoltaics) in particular, it was created an alliance of nations and states committed to moving the world from burning coal to cleaner power sources was a promising sign at COP23 \cite{Jager-Waldau}. 
%%%%%Decarbonization of our energy supply is an important component to achieve the targets, because 65.3\% of the worlds current CO\textsubscript{2} emissions (from energy supple) are due to burning fossil fuels according with 2016 data: 81.1\% of our total primary energy supply depended on burning fossil fuels, namely 27.1\% coal, 31.9\% oil and 22.1\% natural gas~\cite{IEAwes2018}. In terms of final energy consumption electricity only accounted for 18.6\%, but was responsible for 32\% of the total CO\textsubscript{2} emissions~\cite{IEAwes2018}. Photovoltaics (PV) is one of the key technology options for implementing the shift to a decarbonized energy supply, because it is abundant, cannot be monopolized  and can be deployed in a modular way almost everywhere on Earth.
%
%Related to poverty alleviation, 
%
%In reality, the biggest barrier to universal energy access is not the capacity to generate electricity, but rather the ability to get energy to those who need it most. The concept of energy poverty and access tends to focus on very small, incremental shifts in the delivery of energy to poor people. The total energy demand of these shifts constitutes only a small fraction of the ‘gap’ between electricity supply in much of Africa versus more industrialised countries, or the gap between the region’s current and projected electricity supply. https://policy-practice.oxfamamerica.org/static/media/files/FINAL_speakingpowertotruth_SH.pdf
%
%%%%%Poverty, in other hand, needs to be addressed through socio-economic development. Poverty %is conceptualized in material terms as not having access to adequate levels of food, water, clothing, shelter, sanitation, health care and education. This 
%%%%%can be translated into people having insufficient income. 
%
%%%%%%%For numerous people around the world, a better life means getting access to basic needs such as food, health services, housing and clean water. None of these basic needs can be provided without energy. Energy is one of the most essential inputs into sustaining people‘s livelihoods. 
Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide. The number of people without electricity access fell below 1 billion for the first time in 2017~\cite{IEAweo2018}. To provide universal electricity for all, decentralized systems, led by solar PV in off-grid and mini-grid systems, will be the least-cost solution for three-quarters of the additional connections needed, but that grid extension will still have a role to play, especially in urban areas~\cite{IEAweo2018}.

%With worldwide over 400GW cumulative installed photovoltaic electricity generation capacity installed by the end of 2017, photovoltaics still is a small contributor to the electricity supply with a little of 2\%, but its importance for our future energy mix is now acknowledged and with the fastest growth (32\% whem compared with 2016 numbers)~\cite{Jager-Waldau}.
%
In order to simulate or evaluate a PV system there are a myriad of specialized tools available in the market, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, Saber, or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}. However, those tools are based on running experiments in simulation models. Simulation %has the advantage of being cheap (if compared to test in real systems) and can be 
is employed before the system design is concluded but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.

Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}. Any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; then, one can try to give a formal proof or otherwise establish that the program meets its specification.

In this study, an updated review about the use of verification tools in electrical systems is performed, and is presented five case studies, where different model checking tools are compared in terms of performance and reliability when validating stand-alone solar PV systems. In order to perform the comparation and case studies, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is used. The project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automatically verified during the formal process. The model checking tools report in which conditions a system does not meet the user requirements. A key benefit to this approach is that it helps in the detection of flaws in the design phase of system development, thereby considerably improving system reliability~\cite{Akram2018}. The case studies are not theoretical and were deployed in 2018, with feedback information collected from monitoring systems and through interview with the dwellers. 
%The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}.
\section{State-of-art in automated verification of Electrical systems}
This section summarizes, in a chronological way, the research done by previous studies related to the subject of this research.

>>>>

\keywords{Automated verification  \and Model Checking \and Electrical systems \and Solar photovoltaic systems.}
\end{abstract}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion for the first time in 2017~\cite{IEAweo2018}. In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the least-cost solution for three-quarters of the additional connections needed; \textcolor{red}{This sentence is unclear... what is the ``role to play''?} however, that grid extension will still have a role to play, especially in urban areas~\cite{IEAweo2018}.

In order to simulate or evaluate a PV system, there are various specialized tools available in the market, e.g. RETScreen, HOMER, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools, e.g. PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}. However, those tools are based on simulation models, which are employed before the system design is concluded; it has the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.

Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective and faster verification in the design process of PV systems~\cite{ClarkeHV18}. In this study, we review verification tools for PV systems and also present five case studies, where different model checking tools are compared in terms of performance and reliability when validating stand-alone solar PV systems.

In order to compare different model checkers, we developed a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter and electrical load. Design requirements as battery autonomy and power demand in addition to weather conditions, as solar irradiance and ambient temperature, are translated as part of that model and automatically checked by the employed verifiers, which report under which conditions a system does not meet the user requirements.

The main contribution of this approach is that it aids to detect design flaws in PV systems, thus considerably improving system reliability~\cite{Akram2018}; our case studies are empirical and they were deployed in 2018 with feedback information collected from monitoring systems via micro-controllers and by means of interviews with dwellers.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{State-of-art in automated verification of Electrical systems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This section summarizes, in a chronological way, the research done by previous studies related to the subject of this research.
